A Motion Blur Resilient Fiducial Marker For Quadcopter Imaging

### 2014-03-06 ECCV/paper.tex
Incorporated Michael's changes, suggestions and many more...

\begin{abstract}
This paper describes the design and evaluation of a binary fiducial marker
for use with low-cost quadcopters.  Fiducial markers are commonly placed
in environments to provide a uniquely identifiable object in the scene.
For quadcopter applications, fiducials are
typically used for evaluating planning algorithms by allowing ground truth
positions in the scene to be detected from the quadcopter's camera. Quadcopters,
however, are subject to quick and unstable motions that can cause significant motion
blur that severely affects the detection rate of existing fiducial markers.
This problem motivated us to design a fiducial that is robust to motion blur.
Our proposed fiducial design uses concentric circles with the observation that
the direction perpendicular to the motion blur direction will be unaffected by
the blur.  As a result, the fiducial code along this direction is recognizable.
The circular design allows this to work for all motion blur directions.  We
detail the design and detection algorithm for our fiducial and show that our
marker can significantly outperform existing fiducial markers in scenes captured with a quadcopter.
\keywords{Fiducials, tracking, recognition under blur}
\end{abstract}

@@

The recent availability of low-cost quadcopters has help to fuel significant efforts in
research focused on unmanned aerial vehicles.  Navigation and planning of
these vehicles is typically performed using onboard inertial sensors and/or
vision based modules that uses visual cues in the real world~\cite{Davison:2007}.
However, to evaluate the effectiveness of navigation methods, artificial
fiducial markers are commonly placed into the environment to provide
additional information that serves for ground-truth
positional measurements (e.g.,\cite{Bosnak:2012,Lim09,Klopschitz:2007}).

In order to be effective, fiducial markers (or simply, fiducials) need
to be easily detected in the scene.  A variety of fiducial markers
have been proposed in the literature
(e.g.,~\cite{NaimarkF02,ARToolkit02,Fiala05,Pitag13,runetag11}).
These take the form of binary codes arranged into rectangular grids (\cite{ARToolkit02,Fiala05})
or other geometric features arranged in predefined spatial patterns
(\cite{NaimarkF02,Pitag13,runetag11}).
Figure \ref{fig:teaser}-top shows an example of the popular ARTag\cite{Fiala05} as
seen from a quadcopter.  A problem for existing fiducials is  that low-cost quadcopters
often exhibit very quick and erratic physical movements that
results in motion blur in the quadcopter's onboard camera.  This motion blur has
an adverse effect on the  recognition of fiducial  markers.  This can be seen in
Figure \ref{fig:teaser}(top) where the ARTag cannot be recognized due to motion
blur. This is not too surprising as most  existing fiducials are not explicitly
designed to handle motion blur.

@@

\noindent\textbf{Contribution:}~~To address these problems, we propose a
fiducial that is designed to be robust to motion blur.  Our design is based on
concentric circles as shown in Figure \ref{fig:teaser}-b.  The design is based
on the observation that motion blur from a quadcopter tends to be linear in
nature.  As such, when our code is blurred, there is no blur in the direction
perpendicular to the direction of motion.   This allows the signature of the
fiducial to remain intact in any direction.  In addition, by using concentric
rings, we can treat the presence or absence of a ring as a bit, allowing us to
assign an code to the marker.  Our experiments show that this design can
significantly outperform existing codes in the face of motion blur. As far as
we are aware, this is the first work to propose a blur resistant marker.

The remainder of this paper is organized as follows.   Section 2 gives an
overview of related work, focused on fiducials as well as the related problem of
tracking.  Section 3 discusses the our design and detection algorithm, by first
examining the performance of existing codes under blur. Section 4 shows several
experiments using quadcopter imagery.  This is followed by a discussion and
summary in Section 5 and 6 respectively.

@@

Our work is related to two areas: fiducial markers and object tracking. We will
briefly discuss work done in both areas.

\begin{figure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{intersense.jpg}
  Intersense\cite{NaimarkF02}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
 \centering
  \includegraphics[width=\linewidth]{pattKanji.pdf}
  ARToolkit\cite{ARToolkit02}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{ARtag.jpg}
  ARTag\cite{Fiala05}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{pifiducial.jpg}
  Pi-Tag\cite{Pitag13}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{our_fiducial}
  Our Fiducial
 \end{subfigure}
 \caption{This figure shows the design of several existing fiducial markers.  While
 suitable for many environments that are not designed to be recognized under blur.}
 \label{fig:previous_work}
\end{figure}

\noindent{\textbf{Fiducials:}}~Figure~\ref{fig:previous_work} shows several 
examples of existing fiducial markers.  Many designs use a two dimensional
barcode inside a rectangular grid. One of the examples of such fiducial is,
ARToolkit\cite{ARToolkit02}, well known toolkit in Augmented Reality (AR)
system. Kato et al.\cite{kato-artoolkit} have demonstrated the use of ARToolkit
to find the pose in video based AR conferencing system. Many AR applications
used ARToolkit due to its simplicity and efficiency.

Fiala et al. \cite{Fiala05} developed a fiducial termed, ARTag, which is a
bi-tonal system consisting of a square border and an interior region filled
with a 6x6 grid of black or white cells. The improvement in ARTag compared to
ARToolkit was detection of corners instead of detection of lines to find
possible pattern. It proved to be more efficient than \cite{ARToolkit02} in
terms of marker recognition rate as well as the number of different patterns
which can be created. But, drawback of ARTag is, under significant amount of
motion blur, corners can not be detected, resulting in non-recognition of tag.

There were also attempts to use circular patterns instead of rectangular, as
the projective transformation of circles, i.e., conics, are invariant with
respective to point of view of camera\cite{runetag11}. Also, such patterns are
more distinguishable from the background scene due to their unique design.

The use of concentric rings was used  by Gatrell et al.\cite{concentric}
for monocular pose estimation as well as object identification in space. Cho et al.
\cite{Cho:2001,Cho97fastcolor} have used multicolor rings instead of
black and white rings\cite{concentric} to increase possible number of fiducials.
These multicolor rings are used in wide area tracking in large scale
applications.

Naimark et al. \cite{NaimarkF02} have combined concentric rings and 2D bar code
in their fiducial named, Circular Data Matrix. It was beneficial in terms of
easy detection of fiducial as well as being able to encode more unique IDs.

All of these fiducials are not recognizable under occlusion.
Bergamasco et al. \cite{runetag11} have divided fiducial into number of
circular dots, and arranged them in circular fashion, named as RUNE-Tag.
RUNE-tags are reportedly detectable even if 50\% of fiducial area is occluded.
Bergamasco et al. have developed another fiducial, named as Pi-Tag
\cite{Pitag13}, using the cross-ratio concept. As cross-ratio is projective
invariant, the detection of Pi-tag is easier than other tags. Also, compared
to RUNE-tag, it uses remarkably less number of circular dots (12 dots instead of
minimum of 43 dots), still recognisable under occlusion.

But again problem with circular fiducials is, it is very difficult to detect
ellipses accurately under significant motion blur. So, under blur, recognition
rate of these fiducials is very low.

Zhang et al.\cite{Zhang:2002} and Claus et al. \cite{ClausF04} have done
quite comprehensive comparative study of various fiducial marker systems with
respect to processing time, recognition rate and accuracy with
respect to viewing angle and distance.

@@

Most tracking methods( \cite{Ross:2008,Wu:2009,Perez02,Mei:2009} ) assume the
image sequence to be blur free. In reality, however, motion blur in video
sequences is often unavoidable. Wu et al.\cite{Wu:2011} have developed
BLUr-driven Tracker (BLUT) framework for tracking motion-blurred targets. BLUT
is based on the observation that although motion blurs degrade the visual
features of the target, they at the same time, provide useful cues about the
movements to help tracking.

@@

\section{Design of Fiducial}

@@

\subsection{Examining Prior Fiducials Under Motion Blur}

@@

To simulate the appearance of the maker as seen by a quadcopter,  we scaled down
ARTag as well as PiTag fiducial to size 150x150. Both fiducials are then blurred
at various orientations with different blurs scales (denoted in pixels).   The
blur motion ranged from 15 to 50 in magnitude, representing small to significant
motion blur. Figure \ref{fig:artag_pitag} shows the visual appearance of the
blurred tags. We then try to detect the markers using the ALVAR
library\cite{alvar} and Pi-Tag library\cite{ros_pitag}.
The table in the left side of Figure
\ref{fig:artag_pitag} shows the recognition rate (in percent) of two fiducial
markers at various blur scales under different orientation.   As we can see,
the PiTag performance quickly diminished under small amounts of blur, however,
at 35 motion blur, ARTag is recognition rate drops to less than 20\%.

@@

\begin{comment}

\begin{minipage}{\textwidth}
  \begin{minipage}[b]{0.49\textwidth}
\captionof{table}{Recognition rate of AR Tag at various blur scales}
\centering
 \begin{tabularx}{0.75\textwidth}{|Y|Y|}
\cline{1-2}
Blur Scale & Recognition Rate(\%) \\ \cline{1-2}
30 & 100\\ \cline{1-2}
35 & 19 \\ \cline{1-2}
40 & 9 \\ \cline{1-2}
45 & 5 \\ \cline{1-2}
50 & 0 \\ \cline{1-2}
\end{tabularx}
\label{tab:ARTag_blur}
 \end{minipage}	
 \begin{minipage}[b]{0.49\textwidth} 	
\captionof{table}{Blur angle range}
\centering
\begin{tabularx}{0.75\textwidth}{|Y|Y|}
\cline{1-2}
Blur Scale & Blur Angle Range \\ \cline{1-2}
30 & 0 -- 90\\ \cline{1-2}
35 & 32 -- 58 \\ \cline{1-2}
40 & 41 -- 48 \\ \cline{1-2}
45 & 41 -- 48 \\ \cline{1-2}
50 & 44 -- 46 \\ \cline{1-2}
\end{tabularx}
\label{tab:artag_blurangle}
 \end{minipage}
\end{minipage}

From Table \ref{tab:ARTag_blur}, it can be clearly seen that performance of
ARTag drastically degrade with increase in blur scale.

We have also analysed the recognition rate along different blur orientations
(from 0 to 90 degrees) at different blur scales. We found that per blur scale,
at certain blur orientations, recognition of ARTag fails. Table shows the range
of blur angles for which we are able to recognise the ARTag at different blur
scales. From Table \ref{tab:artag_blurangle}, it can be seen that, when blur
scale is greater than 30, ARTag is not recognisable with horizontal blur
orientation(blur angle near zero degrees) as well as vertical blur
orientation(blur angle near 90 degrees).

We have performed blur simulation experiment on Pi-tag \cite{Pitag13} to find
how blur effects circular patterns. We tried to detect blurred Pi-tag using
\cite{ros_pitag}.

\begin{figure}
\begin{subfigure}[b]{0.3\textwidth}
  \centering
  \includegraphics[width=\linewidth]{detect_noblur.jpg}
  No Blur
 \end{subfigure}
 \begin{subfigure}[b]{0.3\textwidth}
  \centering
  \includegraphics[width=\linewidth]{detect_blur15.jpg}
  Blur Scale = 15
 \end{subfigure}
 \begin{subfigure}[b]{0.3\textwidth}
  \centering
  \includegraphics[width=\linewidth]{nodetect_blur20.jpg}
  Blur Scale = 20
 \end{subfigure}
 \caption{Effect of blur on detection of Pi-Tag}
 \label{fig:pitag_blur}
\end{figure}

From Figure \ref{fig:pitag_blur}, it can be seen that, Pi-tag detection
fails when blur scale is more than 15. The reason behind this is, Pi-tag
detection is based on Ellipse detection which will fail in the presence of
significant amount of blur. So, ellipse detection may not be the efficient way
to detect circular patterns under blur.
\end{comment}

We have designed a fiducial that can be considered as a binary code.  The design
uses concentric white rings of equal widths on a black background with a
blurred border\footnote{This design can be easily inverted to have a white
background with white rings}. The outermost and innermost rings represent the
start and end of the code and is embedded in the fiducial.  The binary code is
represented by the presence (or absence) of rings between ``marker'' rings.

\begin{figure}
\centering
  \includegraphics[width=.22\linewidth]{newconcentric_00.pdf}
  \includegraphics[width=.22\linewidth]{newconcentric_01.pdf}
  \includegraphics[width=.22\linewidth]{newconcentric_10.pdf}
  \includegraphics[width=.22\linewidth]{newconcentric_11.pdf}
  \caption{Two bit binary coded fiducials (from left to right: binary code 00,
  binary code 01, binary code 10, binary code 11)}
  \label{fig:fiducials}
\end{figure}

Depending on which ring is present or absent, the resulting binary code will
change. The number of different patterns depends on the number of bits in the
binary code. For example, if the binary code has three bits, there will be a
maximum of three rings between``marker'' rings and we end up with eight
different patterns. Figure \ref{fig:fiducials} shows two bit binary coded
fiducials.

@@

Our fiducial detection strategy is different from \cite{NaimarkF02,Pitag13} and works
under significant amounts of blur.   As previously mentioned, our approach works
 under the assumption that the motion blur on the camera mount on the quadcopter
 can be modelled as linear motion.  This assumption about the motion blur has been shown to be
 reasonable in prior works targeting camera motion blur (e.g.~\cite{Moshe:2003,Moshe:2004}).
Under this assumption, the scene content perpendicular to the blur direction is
unaffected by the blur.  Because of our circular design, this means the
perpendicular direction can be observed as a unblurred linear pattern.  Figure
\ref{fig:blur_direction} shows an example with various motion directions.

We give a brief overview of our algorithm here and details to each step in the
following. Figure \ref{fig:overall_flow} shows the process involved in fiducial
detection process. Our detection algorithm has four steps. First, we apply a
Gabor filter (Step 1) on the image captured through AR Drone. Next, we find the
clusters of patches found in Gabor output using hierarchical clustering (Step
2). Later, we perform Principal Component Analysis (PCA) on each cluster, to
find the blur invariant direction (Step 3). The intensity profile along this
direction is found in the original image. And finally, we match this intensity
profile with training data using K-Nearest neighbor classifier (Step 4).

\begin{comment}
Overall flow of fiducial detection algorithm can be summarised as follows:

\begin{itemize}
  \item Apply Gabor filter on input image
  \item Find connected components in Gabor output
  \item Cluster the connected components into bounding boxes
  \item Detect code in the bounding box
  \begin{itemize}
    \item Run PCA on Gabor output in bounding box
    \item Find intensity profile along first principal component passing through
    centroid
    \item Classify the detected code by training examples
    standards.
  \end{itemize}
\end{itemize}
\end{comment}

\begin{figure}[ht!]
\includegraphics[width=\linewidth]{overall_flow.pdf}
\caption{The flow of our algorithm to detect and classify fiducial in the scene
captured from AR Drone. Four step process includes Gabor Filter(Step 1),
Hierarchical Clustering (Step 2), PCA (Step 3) and Classification using
K-Nearest Neighbor (KNN) classifier (Step 4). Training data for KNN classifier is gathered
offline.}
\label{fig:overall_flow}
\end{figure}

\noindent Details of each of the steps are as follows:\\
\noindent\textbf{Gabor filter}: A 2D Gabor filter is a Gaussian kernel function
modulated by a sinusoidal plane wave. It is used to find high gradient patches from the
image. In our case, it will detect blur invariant sections of the fiducials. We
have applied Gabor filter for eight different orientations ($\theta = 0, 45,
90, 135, 180, 225, 270, 315$). We have used following parameters for
creating each Gabor kernel: $\lambda = 8$, $\gamma = 0.5$, $\sigma =
0.56\lambda$, $\psi = 0 \text{(for real part)}, \pi/2 \text{(for imaginary
part)}$.
Then L2 norm of outputs along all orientations is calculated and finally L2
normed image is binarized.

\noindent\textbf{Clustering}: Connected components are found from the Gabor
output.
These connected components are then clustered in hierarchical fashion, to find
the group of closely positioned patches.

\noindent\textbf{PCA}: Principal Component Analysis is done on the clustered
Gabor output. Along first principal component, intensity profile in the original image
is found. Number of transitions in the intensity profile will give us the
number of rings.

\noindent\textbf{Classification}: Each synthetic fiducial pattern is blurred
along 36 orientations (0, 10, 20, \ldots , 350) and intensity profile along first
principal component from every output is taken as training data for that
fiducial pattern. Process of creation of training data for fiducial with
code ``01'' is depicted in Figure \ref{fig:training_data}. Test pattern is matched
against training data using K-Nearest Neighbor Classifier (K=5) to output class label.

\begin{figure}[h!]
\centering
  \includegraphics[width=\linewidth]{training_data.pdf}
  \caption{Process to create training data for the fiducial pattern with binary
  code ``01''. Synthetic pattern is blurred along various orientations. Gabor
  filter is applied on the blurred pattern. Intensity profile is found along the
  first principal component of the clustered Gabor output. Same process is used
  to create training data for other fiducial patterns.}
  \label{fig:training_data}
\end{figure}

To increase classification accuracy, training data for patterns having same
number of rings is grouped together; e.g., in two bit binary coded fiducial,
training data for pattern ``01'' and ``10'' will be grouped together, In three
bit binary coded fiducial, training data for pattern “001”, “010” and “100” will
form one group while training data for pattern “110”, “011” and “101” will be
in other group, etc. Now, Depending on the number of detected rings in test
pattern, it is matched against corresponding group of training data, again
using  K-Nearest Neighbor Classifier. In this way, if we detect either zero
rings or maximum possible rings in the test pattern, there will be no need to do
further classification.

@@

We have implemented our algorithm in C++ using OpenCV library.
Experiments were performed on a PC with Intel Core i7 processor(@3.4GHz) and 4GB RAM.
Source code and data sets in this paper will be made publicly available.

Our system has been tested several image sequences captured from AR Drone
quadcopter. Each image sequence contains frames containing different fiducial
pattern. Sample output for each fiducial pattern is shown in Figure
\ref{fig:output0} -- Figure \ref{fig:output3}. Our detection process takes
around 0.3 seconds and can handle three to four frames per second.

\begin{figure}[hb!]
\begin{subfigure}{\textwidth}
\centering
  \includegraphics[width=0.48\linewidth]{output_00.jpg}
  \includegraphics[width=0.48\linewidth]{new_results/output_00.jpg}
  \caption{Binary code ``00''}
  \label{fig:output0}
\end{subfigure}
\begin{subfigure}{\textwidth}
\centering
  \includegraphics[width=0.48\linewidth]{output_01.jpg}
  \includegraphics[width=0.48\linewidth]{new_results/output_01.jpg}
  \caption{Binary code ``01''}
  \label{fig:output1}
\end{subfigure}
\begin{subfigure}{\textwidth}
\centering
  \includegraphics[width=0.48\linewidth]{output_10.jpg}
  \includegraphics[width=0.48\linewidth]{new_results/output_10.jpg}
  \caption{Binary code ``10''}
  \label{fig:output2}
\end{subfigure}
\begin{subfigure}{\textwidth}
\centering
  \includegraphics[width=0.48\linewidth]{output_11.jpg}
  \includegraphics[width=0.48\linewidth]{new_results/output_11.jpg}
  \caption{Binary code ``11''}
  \label{fig:output3}
  \end{subfigure}
  \caption{Sample outputs for two bit binary coded fiducials on different
  datasets. Class label attached to the detected fiducial is decimal equivalent
  of the binary code embedded in the detected fiducial.}
\end{figure}

@@

\subsection{Comparison}
We will compare our results with standard fiducials such as ARTag. Also, we will
compare our results with Blur driven tracker(BLUT)\cite{Wu:2011}.
\subsubsection{Comparison with ARTag:}
First, we have repeated blur simulation experiment on our fiducials too, i.e.,
we have downsized our fiducial to size 150x150 and blurred it along various
orientations with different blur scales. Then, we tried to detect the patterns
using algorithm presented in earlier section. The comparison of recognition
rate is shown in Figure \ref{fig:recognition_rate}.

>>>>

\begin{abstract}
This paper describes the design and evaluation of a binary fiducial marker
for use with low-cost quadcopters.  Fiducial markers are commonly placed
in environments to provide a uniquely identifiable object in the scene.
For quadcopter applications, fiducials are
often used for evaluating planning algorithms by allowing ground truth
positions in the scene to be detected from the quadcopter's camera. Quadcopters,
however, are subject to quick and unstable motions that can cause significant motion
blur that severely affects the detection rate of existing fiducial markers.
This problem motivated us to design a fiducial that is robust to motion blur.
Our proposed fiducial design uses concentric circles with the observation that
the direction perpendicular to the motion blur direction will be unaffected by
the blur.  This allows the fiducial code along the blur direction to be recognized.
The circular design allows this to work for all motion blur directions.  We
detail the design and detection algorithm for our fiducial and show that our
marker can significantly outperform existing fiducial markers in scenes
captured with a quadcopter.
\keywords{Fiducials, tracking, recognition under blur}
\end{abstract}

@@

The recent availability of low-cost quadcopters has help to fuel significant efforts in
research focused on unmanned aerial vehicles.  Navigation and planning of
these vehicles is typically performed using onboard inertial sensors and/or
vision based modules that uses visual cues in the real world~(e.g.
\cite{Davison:2007,Engel12,Engel13}). However, to evaluate the effectiveness of
navigation methods, fiducial markers are commonly placed into the environment
to provide additional information that serves for ground-truth
positional measurements (e.g.,\cite{Bosnak:2012,Lim09,Klopschitz:2007}).

In order to be effective, fiducial markers (or simply, fiducials) need
to be easily detected in the scene.  A variety of fiducial markers
have been proposed in the literature
(e.g.,~\cite{NaimarkF02,ARToolkit02,Fiala05,Pitag13,runetag11}).
These take the form of binary codes arranged into rectangular grids (\cite{ARToolkit02,Fiala05})
or other geometric primitives arranged in predefined spatial patterns
(\cite{NaimarkF02,Pitag13,runetag11}).
Figure \ref{fig:teaser}-(a) show the popular ARTag\cite{Fiala05} as
seen from a quadcopter.  A problem for existing fiducials is that low-cost quadcopters
often exhibit very quick and erratic physical movements that
results in motion blur in the quadcopter's onboard camera.  This motion blur has
an adverse effect on the  recognition of fiducial  markers.  This can be seen in
Figure \ref{fig:teaser}-(b) where the ARTag cannot be recognized due to motion
blur. This is not too surprising as most  existing fiducials are not explicitly
designed to handle motion blur.

@@

\noindent\textbf{Contribution:}~~To address these problems, we propose a
fiducial that is designed to be robust to motion blur.  Our design is based on
concentric circles as shown in Figure \ref{fig:teaser}-(c,d).  The design is based
on the observation that motion blur from a quadcopter tends to be linear in
nature.  As such, when our code is blurred, there is no blur in the direction
perpendicular to the direction of motion.   This allows the signature of the
fiducial to remain intact in any direction.  In addition, by using concentric
rings, we can treat the presence or absence of a ring as a bit, allowing us to
assign a code to the marker.  Our experiments show that this design can
significantly outperform existing codes in the face of motion blur. As far as
we are aware, this is the first work to propose a blur resistant marker.

The remainder of this paper is organized as follows.   Section 2 gives an
overview of related work related to fiducials as well as the related problem of
tracking.  Section 3 discusses the our design and detection algorithm as well as 
examining the performance of existing codes under motion blur. Section 4 shows several
experiments using quadcopter imagery.  This is followed by a discussion and
summary in Section 5 and 6 respectively.

@@

Our work is related to two areas: fiducial markers and object tracking. We
briefly discuss work done in both areas.

\begin{figure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{intersense.jpg}
  Intersense\cite{NaimarkF02}
 \end{subfigure}
 \begin{subfigure}[b]{0.14\textwidth}
 \centering
  \includegraphics[width=\linewidth]{pattKanji.pdf}
  ARToolkit\cite{ARToolkit02}
 \end{subfigure}
 \begin{subfigure}[b]{0.14\textwidth}
  \centering
  \includegraphics[width=\linewidth]{ARtag.jpg}
  ARTag\cite{Fiala05}
 \end{subfigure}
 \begin{subfigure}[b]{0.14\textwidth}
  \centering
  \includegraphics[width=\linewidth]{pifiducial.jpg}
  Pi-Tag\cite{Pitag13}
 \end{subfigure}
 \begin{subfigure}[b]{0.14\textwidth}
  \centering
  \includegraphics[width=\linewidth]{our_fiducial}
  Our Fiducial
 \end{subfigure}
 \caption{This figure shows the design of several existing fiducial markers.  While
 each codes have their own pros and cons of various environments, none are designed to be recognized under motion blur.}
 \label{fig:previous_work}
\end{figure}

\noindent{\textbf{Fiducials:}}~Figure~\ref{fig:previous_work} shows several
examples of existing fiducial markers.  Many designs use a two dimensional
barcode inside a rectangular grid. One examples of such a fiducial is from the 
ARToolkit~\cite{ARToolkit02}, a well known toolkit used in many augmented reality (AR) applications. Kato et al.\cite{kato-artoolkit} demonstrated the use of ARToolkit
to find the pose in video based AR conferencing system.

Fiala et al. \cite{Fiala05} proposed a fiducial termed, ARTag, which is a
bi-tonal system consisting of a square border and an interior 6$\times$6 grid of black or white cells. The improvement in ARTag compared to
ARToolkit was detection of corners instead of detection of lines to find
possible pattern. This proved to be more efficient than \cite{ARToolkit02} in
terms of marker recognition rate as well as the number of different patterns
which can be created.   The reliance on both line and corner detection hampers recognition under motion blur.

There were also attempts to use circular patterns instead of rectangular. 
The use of concentric rings was used  by Gatrell et al.\cite{concentric}
for monocular pose estimation as well as object identification in space. Cho et al.
\cite{Cho:2001,Cho97fastcolor} have used multicolor rings instead of
black and white rings\cite{concentric} to increase possible number of fiducials.
These multicolor rings are used in wide area tracking in large scale
applications.  While based on a concentric rings, these particular approaches require 
the full ring to be recognized which is not possible when the pattern undergoes directional
motion blur.

Naimark et al.~\cite{NaimarkF02} proposed a circular bar code
called the, Circular Data Matrix that is beneficial in terms of
easy detection and ability to have a large number
of uniquely identifiable codes.  Addressing the issue of occlusion, 
Bergamasco et al. \cite{runetag11} proposed the RUNE-tag fiducial divided into number of
circular dots arranged them in circular fashion.
RUNE-tags can be detected even when up to 50\% of fiducial area is occluded.
Bergamasco et al.~\cite{Pitag13} proposed the Pi-Tag fiducial also composed 
of circular structures but arranged in a rectangle to exploit projective invariant cross-ration.
This provided similar occlusion resistance as RUNE-tag but with even less
circular dots. All of these techniques however relies on generic features
(e.g., circle detection) that break down under motion blur.

%Zhang et al.\cite{Zhang:2002} and Claus et al. \cite{ClausF04} have done
%quite comprehensive comparative study of various fiducial marker systems with
%respect to processing time, recognition rate and accuracy with
%respect to viewing angle and distance.

@@

Most tracking methods(~\cite{Ross:2008,Wu:2009,Perez02,Mei:2009} ) assume the
image sequence to be blur free. In reality, however, motion blur in video
sequences is often unavoidable. To this end, Wu et al.\cite{Wu:2011} proposed the
Blur-driven Tracker (BLUT) framework for tracking motion-blurred targets. BLUT
is based on the observation that although motion blurs degrade the visual
features of the target, they at the same time, provide useful cues about the
movements to help tracking.

@@

\section{Design of Blur Resistant Fiducial}

@@

\subsection{Examining Prior Fiducials Under Motion Blur}\label{sec:blurtest}

@@

To simulate the appearance of the maker as seen by a quadcopter,  we scaled down
the ARTag and PiTag fiducials to be size 150$\times$150 pixels. Both fiducials are then blurred
using linear motion blur at various orientations with different blurs scales.  
The blur motion ranged from 15 to 50 in magnitude (denoted in pixels),
representing small to significant motion blur. Figure \ref{fig:artag_pitag}
shows the visual appearance of the blurred tags.  We then try to detect the
markers using the ALVAR library~\cite{alvar} and Pi-Tag
library~\cite{ros_pitag}. The table in the left side of
Figure~\ref{fig:artag_pitag} shows the recognition rate (in percentage) of two
fiducial markers at various blur scales over all the different orientation.  
As we can see, the PiTag performance quickly diminished under small amounts of
blur, however, at 35 motion blur, ARTag is recognition rate drops to less than 20\%.

@@

We have designed binary coded fiducial that uses concentric white rings of
equal widths on a black background with a blurred border\footnote{This design
can be easily inverted to have a white background with white rings}. The
outermost and innermost rings represent the start and end of the code and is
embedded in the fiducial.  The binary code is represented by the presence (or
absence) of rings between ``marker'' rings.

\begin{figure}
\centering
  \includegraphics[width=.18\linewidth]{newconcentric_00.pdf}
  \includegraphics[width=.18\linewidth]{newconcentric_01.pdf}
  \includegraphics[width=.18\linewidth]{newconcentric_10.pdf}
  \includegraphics[width=.18\linewidth]{newconcentric_11.pdf}
  \caption{Two bit binary coded fiducials (from left to right: binary code 00,
  binary code 01, binary code 10, binary code 11.)}
  \label{fig:fiducials}
\end{figure}

Depending on which ring is present or absent, the resulting binary code will
change. The number of different patterns depends on the number of bits in the
binary code. For example, if the binary code has three bits, there will be a
maximum of three rings between marker-rings and we end up with eight
different patterns. Figure \ref{fig:fiducials} shows a two bit binary coded
fiducials.

@@

Our fiducial detection strategy is different from \cite{NaimarkF02,Pitag13} and works
under significant amounts of blur.   As previously mentioned, our approach works
under the observation that the motion blur for the quadcopter's camera
can be well modelled as linear motion.  This  linear motion blur assumption has been shown to be
reasonable in prior works targeting camera motion blur (e.g.~\cite{Moshe:2003,Moshe:2004}).
Under this assumption, the scene content perpendicular to the blur direction is
unaffected by the blur.  Because of our circular design, the
direction perpendicular to the linear motion will appear as an unblurred linear
pattern.  Figure \ref{fig:blur_direction} shows examples of this using a
pattern  with various motion directions.

Figure \ref{fig:overall_flow} shows the process involved in fiducial
detection process. We give a brief overview of our algorithm here and details
to each step in the following.  Our detection algorithm has four steps. Step 1,
we apply a Gabor filter on the image captured through AR Drone to isolate the
potential locations of the pattern.  Step 2, we find the clusters of patches
found in Gabor output using spatial clustering.  Step 3, performs Principal
Component Analysis (PCA) on each cluster to find the dominate direction
unaffected by blur.  Step 4, based on the direction we extract the intensity
profile of the pattern and classify the code using a K-Nearest neighbor
classifier based on training data.

\begin{figure}[ht!]
\includegraphics[width=\linewidth]{overall_flow.pdf}
\caption{An overview of our algorithm to detect and classify fiducial. 
The four step process includes (Step 1) Gabor filtering,
(Step 2) component clustering, (Step 3) PCA to determine the dominate direction, 
and (Step 4) KNN classification using training-data captured for each pattern.}
\label{fig:overall_flow}
\end{figure}

\noindent Details of each of the steps are as follows:\\
\noindent\textbf{Gabor filter}: A 2D Gabor filter is a Gaussian kernel function
modulated by a sinusoidal plane wave~\cite{Kruizinga:2002}. It is used to find
high gradient patches from the image. In our case, it is used to detect blur
invariant sections of the fiducials. We have applied Gabor filter for eight
different orientations ($\theta = 0, 45, 90, \ldots ,225, 270, 315$).  The
following parameters where used for creating each Gabor kernel: $\lambda$ (wavelength) $= 8$, $\gamma$
(aspect ratio) $= 0.5$, $\sigma$ (spread) $= 0.56\lambda$, $\psi$
(phase angle) $= 0$ (for real part), $\pi/2$ (for imaginary part).
Then L2 norm of outputs along all orientations is calculated and finally L2
normalized image is thresholded with threshold set to $0.4$ (on scale of zero to
one).

\noindent\textbf{Clustering}: The binarized Gabor filter response are
treated as a set of connected components in the image.   This clustering
stage is to find components that are located in a close spatial region.  We do
this by using hierarchical fashion clustering~\cite{ALGLIB}. We used unweighted
average linkage with distance threshold set to 150 for merging clusters in
hierarchical fashion.

\noindent\textbf{PCA}: For each clustered set of components, we apply 
PCA to determine the dominate direction.  This is done by examining the
orientation of the first principal component.  We then extract an intensity
profile patch in the input image along this direction as it extends through the
bounding box of the cluster. The signature of this profile will be used to
identify the code.

\noindent\textbf{Classification}: As mentioned above, a small image patch containing
the intensity profile of the fiducial is used to identify the code.   We found
that a training-based method using KNN gave better results than trying to directly determine
the number of transitions in the image patch.  To build the training-data, a
synthetic fiducial pattern is blurred along 36 orientations (0, 10, 20, \ldots
, 350) and its intensity profile along the first principal component from every
output is taken as training data for that fiducial pattern. Figure
\ref{fig:training_data} shows the process of creating this training data for
``01'' fiducial with.  For an input image patch, we normalize its intensity
range and then compare it against the training-data. The class label from the
closest top $K=5$ images in the training-data is used to label the patch.

\begin{figure}[h!]
\centering
  \includegraphics[width=\linewidth]{training_data.pdf}
  \caption{Process to create training data for the fiducial pattern with binary
  code ``01''. The synthetic pattern is blurred along various orientations. Gabor
  filter is applied on the blurred pattern. Intensity profile is found along the
  first principal component of the clustered Gabor output. Same process is used
  to create training data for other fiducial patterns.}
  \label{fig:training_data}
\end{figure}

To increase the classification accuracy, training data for patterns having same
number of rings is grouped together; e.g., in two bit binary coded fiducial,
training data for pattern ``01'' and ``10'' will be grouped together, In three
bit binary coded fiducial, training data for pattern ``001'', ``010'' and
``100'' will form one group while training data for pattern ``110'', ``011'' and
``101'' will be in other group, etc. Now, depending on the number of detected
rings in test pattern, it is matched against corresponding group of training data, again
using  K-Nearest Neighbor Classifier. In this way, if we detect either zero
rings or maximum possible rings in the test pattern, there will be no need to do
further classification.

@@

We have implemented our algorithm in C++ using OpenCV library.
Experiments were performed on a PC with Intel Core i7 processor(@3.4GHz) and 4GB RAM.
Source code and data sets in this paper will be made publicly available.  Video clips
have also been provided in the supplemental materials.

Our system has been tested on several image sequences captured from an AR Drone
quadcopter.  The Drone was flown indoors looking at patterns attached to various walls.
Each image sequence contains frames containing different fiducial
patterns. Sample output for each fiducial pattern is shown in Figure
\ref{fig:output0} -- Figure \ref{fig:output3}. Our detection process takes
around 0.3 seconds which translates to around three to four frames per second.

@@

\subsection{Comparisons}

We compare our results with the commonly used ARTag. We also compare 
our results with Blur-driven tracker (BLUT)\cite{Wu:2011}.
\subsubsection{Comparison with ARTag}
First, we have repeated blur simulation experiment on our fiducials as reported
in Section~\ref{sec:blurtest}.  Specifically, we build our blur resistant
patterns size 150x150 and blurred them along various orientations with different
blur scales. Then, we tried to detect our fiducial using a 2-bit patterns using
algorithm presented in earlier section.

\begin{figure}
\includegraphics[width=\linewidth]{blur_maximum.pdf}
\caption{Result of our fiducial detection algorithm on blur simulated data}
\label{fig:blur_maximum}
\end{figure}
